\input{ActionIntro.tex}

\cleartoleftpage

%courage to act

\smallQuote{BD_ACT}{Action may not always bring happiness, but without action there is none.}{Benjamin Disraelli}{}

\smallQuote{MG_ACT}{You may never know what results come from your action but if you do nothing there will be no result.}{Mahatma Ghandi}{}

\cleartorightpage
\HugeQuote{MG_AEP}{Action expresses priority}{}{Mahatma Ghandi}{}{}


\hugeQuote{FB_CWA}{Code wins.}{}{}{}{}
\hugeQuote{LT_FAT}{Fac aut tace.}{}{}{}{Do or be silent.}
\hugeQuote{RG_DDX}{Demonstrate}{\newline don't explicate.}{Robert Greene}{}{}
\cleartorightpage
\HugeQuote{YB_FORK}{When you come to a fork in the road}{, take it.}{Yogi Bera}{}{}

\cleartoleftpage
%focus on what you can do 
\smallQuote{MA_NOW2}{Stick to what's in front of you; \newline
Idea, action, utterance.}{Marcus Aurelius}{}{}

\smallQuote{MA_NOW1}{Each of us lives only now in this brief instant. The rest has been lived already or is impossible to see.}{Marcus Aurelius}{}


\smallQuote{MA_CREDIT}{Do what nature demands. Get a move on if you have it in you and don't worry whether anyone will give you any credit for it.
And don't go expecting Plato's \say{Republic} either, just be satisfied with even the smallest progress.}{Marcus Aurelius}{}

\cleartorightpage
\hugeQuote{RG_PROBLEM}{When you confront a problem}{ you begin to solve it.}{Rudy Guilliani}{BW_TALK}{}

\hugeQuote{HT_CREDIT}{It's amazing what you can accomplish}{ if you don't care who gets the credit.}{Harry S Truman}{}{}

\cleartorightpage
\HugeQuote{JL_LIFE}{Life is what happens}{ while you are busy making other plans.}{John Lennon}{}{}

%consistency
\cleartoleftpage
\HugeQuote{RH_HABIT}{How you do anything is how you do everything.}{}{Ryan Holiday}{}{}

\HugeQuote{MLK_HABIT}{If I cannot do great things}{ I can do small things in a great way.}{Martin Luther King Jr.}{}{}



\cleartoleftpage

\HugeQuote{JVG_ACT}{To think is easy}{.\newline
To act is hard.\newline
But the hardest thing of all is to act in accordance with your thinking.}{John Von Goethe}{}{}

\cleartorightpage

\HugeQuote{MR_ACT}{Although understanding the theory behind the action enables one to speak}{, it is the practice which enables one to act.}{Musonius Rufus}{}{}

\cleartorightpage
\HugeQuote{AR_HABIT}{Quality is not an act.}{\newline
It is a habit.}{Aristotle}{}{}