
\input{FocusIntro.tex}

\cleartorightpage
\HugeQuote{CYM}{Call your mom.}{}{}{}
 
\cleartoleftpage

%company and how you spend your time

\smallQuote{LC_COMPANY}{You are whatever the company you keep is.}{Lord Chesterfield}{}{}
\smallQuote{C_HONOR}{Let your mind dwell on examples of honour.}{Cicero}{}{} % cf machiavelli ?

\smallQuote{RH_LIFERS}{Steer clear of lifers, the toxic and charlatans.\newline You become who you know.}{Ryan Holiday}{}

\smallQuote{PG_PB}{Relentlessly prune bullshit, don't wait to do things that matter, and savor the time you have. That's what you do when life is short\llink{http://www.paulgraham.com/vb.html}.}{Paul Graham}{}

%todo: plenty of space above
\cleartorightpage
\HugeQuote{T_GM}{From good men you will learn good things}{, if you mix with bad men you will destroy even your existing sense.}{Theognis}{}{} 

\cleartorightpage
\HugeQuote{PL_DST}{Don't spend time on people you don't like.}{}{Prue Leith}{}{}
\cleartoleftpage

\HugeQuote{H_OWN}{They should try to subordinate things to themselves}{ not themselves to things.}{Horace}{}{}

\HugeQuote{FC_OWN}{The things you used to own}{. Now they own you.}{Jack, Fight Club}{}{}

\cleartoleftpage

\HugeQuote{FP_BACK}{It's a long road there's no turning back.}{}{Dr. Jeff Cameron}{} % Sampled by Funki Porcini

\HugeQuote{HDT_BACK}{Never look back}{ unless you're planning to go that way.}{Henry David Thoreau}{}{}

%TODO possibly humility ? 
% \smallQuote{GBS_CBD}{Those who say it cannot be done should not interrupt those who are doing it.}{George Bernard Shaw}{MA_NOW2}{}

%task selection
\cleartoleftpage	
\smallQuote{DA_CDA}{You can do anything.\newline but you can't do everything.}{David Allen}{MA_SMALL}
% \smallQuote{BC_RYP}{Reaching your true potential involves choice. \newline How exactly you choose to excel is up to you.}{Brian Colbert}{}

\smallQuote{BJ_DWYL}{If you're not doing what you love,\newline
you're wasting your time.}{Billy Joel}{OW_HW}

\smallQuote{GBS_PIGS1}{Never wrestle with pigs,\newline
you both get dirty and the pig likes it.}{George Bernard Shaw}{RH_PIGS2}

\smallQuote{UB_DL}{Photography is a subtractive process, you start with the whole world and finish with a small square of it.}{Uta Birth}{TF_SLO}

%\smallQuote{HC_DL}{What you choose to exclude is just as inportant as what you choose to include.}{Henry Carroll}{} 

%todo: position
% \smallQuote{MA_NOW1}{Each of us lives only now in this brief instant. The rest has been lived already or is impossible to see.}{Marcus Aurelius}{}

 
\cleartorightpage
\hugeQuote{MT_NOMFUP}{NoMFuP}{}{Malcolm Tucker}{ST_UTU}{}
\hugeQuote{MA_NRA}{No random actions}{, none not based on underlying principles.}{Marcus Aurelius}{}{}
\hugeQuote{EP_FOOL}{If you wish to improve}{, be content to appear clueless in extraneous matters.}{Epictetus}{}{}

\cleartoleftpage
\HugeQuote{TF_SLO}{Slow down}{ and remember this; most things make no difference. Being busy is a form of laziness. Lazy thinking and indiscriminate action.}{Tim Ferriss}{MA_DL}{
See: efficacy hacks\llink{http://bit.ly/1EDPjUQ} and a not to do list\llink{http://bit.ly/1EDPu2H}.
}

\HugeQuote{MA_DL}{If you seek tranquillity, do less}{ or (more accurately) do what's essential because most of what we say and do is not essential.\newline
Ask yourself at every moment \say{is this necessary?}}
{Marcus Aurelius}{}{}

\cleartoleftpage
\HugeQuote{MA_SMALL}{You're better off not giving the small things more time than they deserve.}{}{Marcus Aurelius}{}

\HugeQuote{PD_DL}{There is nothing so useless}{ as doing efficiently that which should not be done.}{Peter Drucker}{}{}

\cleartorightpage
\HugeQuote{LT_DL}{Choose one}{,\newline
reject the other.}{Lao Tzu}{}{}

%\hugeQuote{MA_NOW2}{Stick to what's in front of you}{;\newline
%Idea, action, utterance.}{Marcus Aurelius}{}{}

% \hugeQuote{MA_OBSERVE}{And so I'll treat them as the law that binds us requires}{. With kindness and with justice.\newline And the inconsequential things?\newline I'll do my best to treat them as they deserve.}{Marcus Aurelius}{}{}
% todo reposition 

\cleartoleftpage
\vspace*{\fill}
\hugeQuote{OW_HW}{Hard work}{ is simply the refuge of people who have nothing better to do.}{Oscar Wilde}{}{}

\hugeQuote{BD_LIFE}{A man is successful}{ if he gets up in the morning, goes to bed at night and in between does what he wants to.}{Bob Dylan}{BJ_DWYL}{}
\vspace*{\fill}

\cleartorightpage
\HugeQuote{PL}{Parkinson's Law}{:\newline
A task will swell in (perceived) importance and complexity in relation to the time allocated for its completion.}{Cyril Northcote Parkinson}{C_ABILITY}{\href{http://bit.ly/1Massqh}{http://bit.ly/1Massqh}}

\cleartoleftpage

\HugeQuote{MA_CUCUMBER}{The cucumber is bitter?}{\newline
Then throw it out.\newline
\newline
Brambles in the path?\newline
Then go around them.}{Marcus Aurelius}{PL_DST}{}

%TODO: unsure on origin here but likely MA
\HugeQuote{SP_HABIT}{Test each thought}{; is it:
\begin{itemize}
\item true?
\item necessary?
\item self indulgent?
\item harmful to others?
\end{itemize}}{}{}{}

\cleartorightpage

\HugeQuote{RH_6MONTHS}{In six months}{ you will have discarded most of what you say is important today.}{Ryan Holiday}{}{}

\cleartoleftpage

\HugeQuote{GKN_WORK}{Successful people are not gifted}{; they just work hard, then succeed. \emph{On purpose.}}{G. K. Nielson}{LR_WORK}{}

%\hugeQuote{WT_WORK}{It sounds a bit square}{, but I've found that the chances of getting a good result are just so much higher when you spend at least eight hours a day on your work.}{Wolfgang Tillmans}{}{}

\cleartorightpage
\HugeQuote{MA_GOAL}{If you don't have a consistent goal in life}{, how can you live it in a consistent way?}{Marcus Aurelius}{}{}

\cleartoleftpage

\HugeQuote{RH_PIGS2}{Never teach a pig to sing.}{\newline
It wastes time and annoys the pig.}{Robert Heinlein}{GBS_PIGS1}{} 

\cleartorightpage
\HugeQuote{TF_HARD}{Sometimes the hard stuff is hard because you shouldn't do it in the first place.}{}{Tim Ferriss}{}{}

