\cleardoublepage
\begin{multicols}{2}

As hard as it can be to take action, it can be even harder to maintain the level of focus we need to on the right things. If the right things are even clear to us. In deciding whether things are worth our time we can consider what impact our efforts will produce (cf. \ref{ST_UTU}), the sun might still hide behind the clouds on our day at the beach, the white van will still drive too close to us no matter how much we hope otherwise. %effort vs impact

Even if we can put all the things we have no control over to one side we still squander our time and energy. We're too polite, putting ourselves and our priorities to one side to avoid offending people (cf. \ref{PL_DST} and \ref{GVG_ALONE}), we make great gains on Twitter and Facebook while we let our Amazing Book Idea gather dust (cf. \ref{MA_SMALL}), wr spend hours mindlessly scrolling around crappy sensationalist journalism when we could be reading a beautifully crafted novel (cf. \ref{TP_BOOK}) or working on our supposedly beloved hobby (cf. \ref{BB_PRACTICE}). 
Epictetus reminds us that we need to gut things from our lives which take us away from the tricky but important business of improvement. We can be sure that nothing truly terrible will happen if we stop using social media or watching 24 hour rolling news with repeats every 25 minutes or so. We can be supremely confident that life will carry on in fine style if we leave the "mind numbing spirit crushing game shows\footnote{Renton, Trainspotting}" to someone else. There are so many ways to spend the time we have, we need to be careful not to waste it and that can require significant effort. Consistently asking ourselves whether what we're doing right now is truly important to us (cf. \ref{MA_DL}) will be exhausting but ultimately incredibly valuable.

Maybe we should call someone who's important to us and focus soley on that for starters. 

Let's take 15 minutes. The advice and guidance on the next few pages will still be here when we get back. 

\end{multicols}
\clearpage
