\input{GenerosityIntro.tex}

\cleartoleftpage

\smallQuote{MA_GIVE}{You've given and they've received it. And yet, like an idiot, you keep holding out for more. To be credited with a good deed? To be repaid in kind? why?}{Marcus Aurelius}{HT_CREDIT}

\smallQuote{BT_GIVE}{Always give without remembering and receive without forgetting.}{Brian Tracy}{S_DO}{}

\smallQuote{MM_HATE}{Resentment is like taking poison and waiting for the other person to die.}{Malachi McCourt}{TS_HHH}

\smallQuote{AL_JWWWB}{They are just what we would be in their situation.}{Abraham Lincoln}{}{} 

\smallQuote{LT_SELF}{No self interest? Self is fulfulled.}{Lao Tzu}{}

%todo review
\smallQuote{PS_RAGE}{Patience Wounded too often becomes rage.}{Publius Syrus}{}

\cleartorightpage

\HugeQuote{MA_TRUST}{The people I deal with today will be}{:
\begin{itemize}
	\item meddling
	\item ungrateful
	\item arrogant
	\item dishonest
	\item jealous
	\item surly
\end{itemize}}{Marcus Aurelius}{SL_GIVE}{People are going to be like that but remember that you've been like that too from time to time.}

%Roman playwright and poet Terence gave voice when he wrote: ‘I am human: nothing human is foreign to me’ 
\cleartoleftpage
\HugeQuote{MA_HATE}{Someone hates me?}{ Their problem.\newline
Mine: to be patient and cheeerful with everyone (including them).}{Marcus Aurelius}{}{}
\cleartorightpage
\HugeQuote{LT_HATE}{People who are good}{, I treat well. People who are not good, I also treat well.}{Lao Tzu}{}{}

\cleartoleftpage
\HugeQuote{S_DO}{Kindness gives birth to kindness.}{}{Seneca}{}{}
\cleartorightpage
\HugeQuote{DL_KINDNESS}{Show kindness whenever possible.}{}{Dalai Lama}{S_DO}{Hint: it's always possible.}

%\hugeQuote{}{Be kind}{, everyone is fighting a hard battle.{John Watson}{}{} 

%\smallQuote{SL_REBEL}{We'll always rebel against certain painful truths. And it's wise to admit this.}{School of Life}{} 

\cleartoleftpage
\hugeQuote{MA_MISTAKE}{That you've made enough mistakes yourself}{. You're just like them.}{Marcus Aurelius}{SL_GIVE}{}


\hugeQuote{MDM_SELF}{If talking to oneself did not look so mad}{ no day would go by without my growling to myself \say{you silly shit!}\newline
Yet, I do not intend that to be the definition of me.}{Michel De Montaigne}{HM_DWW}{}

\cleartorightpage

\HugeQuote{SL_GIVE}{Forgiveness means a long memory of all the times when we wouldn't have gotten through life with someone cutting us some slack.}{ It is recognising that living with others is not possible without excusing errors.}{School of Life}{}{See the modern virtues \llink{http://bit.ly/1XoP0tE}}
%http://thephilosophersmail.com/wp-content/uploads/2014/04/Ten-Virtues.pdf


\cleartoleftpage
\hugeQuote{EC_FTP}{Never say that people are evil.}{ You just need to find the pin.}{\'{E}mile-Auguste Chartier}{} 

\hugeQuote{WD_JUDGE}{When you judge another}{ you do not define them, you define yourself.}{Wayne Dyer}{MA_JUDGE}{}

\HugeQuote{E_ISR}{It seemed right to him.}{}{Epictetus}{}{}

\cleartorightpage
\HugeQuote{H_RAZOR}{Hanlon's Razor}{: \newline
Never attribute to malice that which can be adequately explained by incompetence.}{Robert J. Hanlon}{SL_GIVE}{or weakness or fear or hunger or \ldots}

%Unsure on which chapter
%\hugeQuote{LT_PAST}{Forgiveness means giving up hope}{ of a better past}{Lily Tomlin}{MA_NOW1}{}

