
\input{GratitudeIntro.tex}

\cleartorightpage
\HugeQuote{S_CUCUMBER}{Get used to your circumstances}{, complain about them as little as possible. Grasp whatever advantages they have to offer.}{Seneca}{MA_CUCUMBER}{}

%% negative Visualisation 
\vspace*{\fill}
\hugeQuote{MDM_LOSS}{Certainly, if a man of understanding still has himself, he has lost nothing.}{}{Michel De Montaigne}{}{}

\hugeQuote{LT_SIMPLE}{Look at plain silk}{; hold uncarved wood. The self dwindles; desires fade.}{Lao Tzu}{}{} 
\vspace*{\fill}
\cleartorightpage 

\HugeQuote{MA_HMYD}{Treat what you don't have as non-existent}{;

	Look at what you have, the things you value most and think how much you'd crave them if you didn't have them.}{Marcus Aurelius}{}{}



%% Awe
\cleartoleftpage

\hugeQuote{RWE_STARS}{If the stars were to appear but one night every thousand years}{ how man would marvel.}{Ralph Waldo Emerson}{}{}

\hugeQuote{RG_WONDER}{The ability to express wonder and amazement}{ and seem like you mean it, is a rare and dying talent but one that is still greatly valued.}{Robert Greene}{RWE_STARS}{}

\cleartorightpage
\HugeQuote{CP_SCAR}{It is so hard to forget pain}{ but it is harder to remember sweetness. There is no scar for happiness.}{Chuck Palaniuk}{}{} %possibly ref MR_WORK

\cleartoleftpage
\HugeQuote{E_MORTAL}{When you kiss your wife}{ or child, repeat to yourself, \newline\say{I am kissing a mortal}}{Epictetus}{}{\ldots and she may be gone tomorrow.}

\cleartorightpage

\HugeQuote{SW_CUSTODIAN}{Of course}{, I never considered myself the owner of these things, only their custodian}{Stefan Zwieg}{}{}

% TODO not the right place at all
%\hugeQuote{MR_WORK}{If you accomplish something good with hard work}{, the labour passes quickly but the good endures; if you do something shameful in pursuit of pleasure, the pleasure passes quickly but the shame endures}{Musonius Rufus}{}{}