\input{HumilityIntro.tex}

\cleartorightpage
\HugeQuote{ME_BEGIN}{Be willing}{ to be a beginner every single morning.}{Meister Eckhart}{EP_FOOL}{}{}

\cleartorightpage
\HugeQuote{FP_WDIK}{Que sais-je?}{}{French phrase via Montaigne}{}{\say{what do I know?}}

%%%life / death

\cleartoleftpage
\vspace*{\fill}
\hugeQuote{MA_LIVE}{You could leave this life right now.}{ Let that determine how you act.}{Marcus Aurelius}{}{}
\hugeQuote{S_DF}{No one has had so much divine favour}{ that they could guarantee themselves tomorow.}{Seneca}{E_MORTAL}{}
\vspace*{\fill}
\cleartorightpage
\HugeQuote{IP_GAME}{After the game}{ the king and the pawn go back into the same box.}{Italian Proverb}{}{}

%%% help
\cleartoleftpage
\HugeQuote{ST_GUIDE}{He who does not employ a guide cannot gain advantage from the ground.}{}{Sun Tzu}{}{}

\cleartorightpage
\HugeQuote{DLP_HELP}{Take the help.}{}{Danielle La Porte}{}{}

\cleartorightpage

\HugeQuote{MDM_WEIGH}{I do not count my borrrowings}{, I weight them.}{Michel de Montaigne}{}{}


%%%fate
\cleartoleftpage
\vspace*{\fill}
\smallQuote{AS_LUCK}{Men of any worth soon come to see that they are in the hands of Fate and gratefully submit to be moulded by its teachings.}{Arthur Schopenhauer}{} 

\smallQuote{MA_ALWAYS}{Everywhere, at each moment, you have the option:
\begin{itemize}
\item to accept this event with humility
\item to treat this person as he should be% treated
\item to approach this thought with care%, so that nothing irrational creeps in
\end{itemize}}{Marcus Aurelius}{WG_JUDGE}{} % E_DLTF
\vspace*{\fill}
\cleartorightpage
\vspace*{\fill}
\hugeQuote{E_LUCK}{Foolish is the man who delights in his good fortune, supposing it will never leave him.}{}{Euripides}{S_ENDURE}{}
\hugeQuote{MT_VISIT}{If you're not humble}{ in this world, then the world will throw huility at you.}{Mike Tyson}{}{}
\vspace*{\fill}
\cleartoleftpage
\HugeQuote{MC_VISIT}{The moment you think you are successful}{, failure will be there for you.}{Maurizio Cattelan}{}{}
\cleartorightpage
\HugeQuote{MA_LUCK1}{To accept it without arrogance}{, to let it go with indifference.}{Marcus Aurelius}{}{}

%growth mindset
\cleartoleftpage
\vspace*{\fill}
\smallQuote{MC_BOAST}{Boasting is what a boy does, because he has no real  effect on the world.}{Matthew Crawford}{C_BOAST}

\smallQuote{C_BOAST}{A superior man is modest in his speech but exceeds in his actions.}{Confucious}{}{}

%TODO review
\smallQuote{GBS_CBD}{Those who say it cannot be done should not interrupt those who are doing it.}{George Bernard Shaw}{}{}% todo check link MA_NOW2
\vspace*{\fill}

\cleartorightpage
\vspace*{\fill}
\hugeQuote{RH_CHANGE}{Your opinion is either dependent on the facts or not;}{\newline
When they change you should shift along with them.}{Ryan Holiday}{JKZ_ENDURE}{The facts were always there, of course, just unclear or hidden. Think clearly about what you're looking at. \S \ref{NT_FAIL}}

\hugeQuote{MA_CHANGE}{Remember that to change your mind}{ and accept correction are mere acts too.}{Marcus Aurelius}{BR_CHANGE}{and so, under our control}
\vspace*{\fill}
%TODO review for position
%\hugeQuote{H_GOD}{To a god}{, the wisdom of the wisest man sounds apish.}{Heracticlus}{}{} 
\cleartoleftpage
\vspace*{\fill}
\hugeQuote{WS_FOOL}{The fool doth think he is wise and the wise man knows himself to be a fool}{}{William Shakespeare}{P_TALK}{}

\hugeQuote{JVG_VALUE}{A great failing}{: to see yourself as more than you are and value yourself at less than your true worth.}{John Von Goethe}{AG_WORK}{} %todo check link to p63 in original notes
\vspace*{\fill}

\cleartorightpage
\HugeQuote{RG_CRITICISM}{Never be so self absorbed}{ as to believe that the master is interested in your criticisms of him, now matter how accurate they are.}{Robert Greene}{}{but always be ready to listen and use the criticism you hear.}


%%%bigger view
\cleartoleftpage
\vspace*{\fill}
\hugeQuote{JS_FOLLY}{It is the folly of many}{ to mistake the echo of a London coffee shop for the voice of a kingdom.}{Jonathan Swift}{}{}
\hugeQuote{JDB_UNNAMED}{The unnamed should not be mistaken for the non-existent.}{}{Jon de la Brug\'{e}re}{}{}
\vspace*{\fill}

\cleartorightpage
\HugeQuote{CTG_COUNSEL}{Diversity in counsel}{.\newline
Unity in command.}{Cyrus the Great}{ST_GUIDE}{} % possibly move to confidence

%\smallQuote{RH_EARN}{We never earn the right to be greedy or to pursue our interests at the expense of everyone else.}{Ryan Holiday}{} 

\cleartorightpage

\HugeQuote{TD_UNIQUE}{You are not a beautiful and unique snowflake.}{}{Tyler Durden}{}{}