
\input{LeadershipIntro.tex}


%sphere of influence
%%%%%%%%%%%%%%%%%%%%
\cleartoleftpage
\vspace*{\fill}

\hugeQuote{FB_WISE}{Wise men make more opportunities than they find.}{}{Francis Bacon}{}{}

\hugeQuote{RLS_SEED}{Don't judge each day by the harvest you reap}{ but by the seeds you sow.}{Robert Louis Stephenson}{}{}

\hugeQuote{SG_JOB}{Our job as leaders} (and we all are, in our own way) is to elevate the long run on behalf of those we care about.}{Seth Godin}{}{}

\vspace*{\fill}
\cleartorightpage

\HugeQuote{MR_NL}{A physician who heals a few}{ is no less a doctor than one who heals many.}{Musonius Rufus}{} 

% Difficulty
%%%%%%%%%%%%
\vspace*{\fill}
\hugeQuote{RH_RAW}{Races are won here not there}{. Where it is hardest to speed up not easiest.}{Ryan Holiday}{}

\hugeQuote{RG_CONFLICT}{The more conflicts and difficult situations you put yourself through}{ the more battle tested your mind will be.}{Robert Greene}{RH_RAW}{}
\vspace*{\fill}

\cleartorightpage
\HugeQuote{BB_PRACTICE}{When you are not practicing}{ remember that someone else is and when you meet him he will win.}{Bill Bradley}{}{}

% right attention
%%%%%%%%%%%%%%%%%

\cleartoleftpage

\smallQuote{RL_LISTEN}{Learning to listen is the most valuable thing you can do.}{Robert Love}{AE_DO}{}

\smallQuote{AC_DO}{As I grow older I pay less attention to what people say, I just watch what they do.}{Andrew Carnegie}{AE_DO}

\smallQuote{MA_LISTEN}{Practice really hearing what people say. Do your best to get inside their minds.}{Marcus Aurelius}{AE_DO}{}

\smallQuote{RG_DO}{Pay less attention to the words people use and greater attention to the tone of their voice, the look in their eyes and their body language.}{Robert Greene}{AE_DO}


\cleartorightpage
\HugeQuote{AE_DO}{People do not change}{, they are merely revealed.}{Anne Enright}{SZ_LESSON}{}


\cleartoleftpage
\vspace*{\fill}
\hugeQuote{TP_UNDER}{Under promise;}{ over deliver}{Tom Peters}{C_BOAST}{}

\hugeQuote{BW_TALK}{There is no use talking about the problem}{ unless you talk about the solution}{Betty Williams}{}{}

\hugeQuote{HF_REP}{You can't build a reputation}{ on what you're going to do.}{Henry Ford}{}{}

\vspace*{\fill} \cleartorightpage
% \hugeQuote{RG_BOAST}{Be careful not to boast}{ of any success.}{Robert Greene}{MC_BOAST}{}

\HugeQuote{SP_QUIET}{Be quiet}{, work hard and\newline
look after yourself.}{}{C_WAIT}{}


% exercise of power
%%%%%%%%%%%%%%%%%%%
\cleartoleftpage

\HugeQuote{SC_BAD}{\texttt{use strict;}}{\newline good servant, bad master.}{Simon Cozens}{}{}

\HugeQuote{LT_CHIEF}{Be the chief}{ but\newline
 never the lord.}{Lao Tzu}{}{}

\HugeQuote{KR_SPORT}{One man practicing sportsmanship}{ is better than 100 teaching it.}{Knute Roche}{HF_REP}{}

\HugeQuote{LT_NPP}{Has self-knowledge without self-display}{\newline
Self-respect without pride.}{Lao Tzu}{}

\cleartorightpage
\HugeQuote{MR_CHIEF}{Kings soon perish}{ who make a habit of justifying their actions to their subjects by saying \say{I have the power} rather than \say{it is my duty}}{Musonius Rufus}{} 



% did what he thought was right  
\cleartoleftpage
\HugeQuote{MA_ASK}{Learn to ask of all actions}{, \say{why are they doing that?}\newline
Starting with your own.}{Marcus Aurelius}{H_RAZOR}{}
 
\HugeQuote{RG_TRUSTYOU}{In the end, if people mistrust you}{ and resist your authority you have only yourself to blame.}{Robert Greene}{}{}

\HugeQuote{MA_CORRECT}{If they've done something wrong}{, gently show them how to improve.\newline
If you can't do that the blame only lies with you.}{Marcus Aurelius}{HT_CREDIT}{}

\HugeQuote{MA_PURPOSE}{To undertake nothing}{ without purpose
or for any other reason than the common good.}{Marcus Aurelius}{TF_SLO}{}{}

% successful completion
%%%%%%%%%%%%%%%%%%%%%%
\vspace*{\fill}

\hugeQuote{RH_CCNC}{Close captures no crowns.}{}{Ryan Holiday}{}{}

\hugeQuote{ES_EFFORT}{Super-human effort}{ is not worth a damn unless it produces results.}{Shackleton}{}{}
\vspace*{\fill} \cleartorightpage
\vspace*{\fill}
\hugeQuote{RG_KNOW}{The ability to measure people}{ and know who you're dealing with is the most important skill of all.}{Robert Greene}{AE_DO}{}

\hugeQuote{CF_DNI}{Do not impose on others}{ what you yourself do not desire.}{Confucious}{}{}
\vspace*{\fill}

%\hugeQuote{RG_WORK2}{Everything is judged by its appearance}{; what is unseen counts for nothing. Do not get lost in the crowd or burried in oblivion.}{Robert Greene}{}{}

%\hugeQuote{CWB_FEEL}{They may forget what you said}{ but they will never forget how you made them feel.}{Carl W. Buechner}{}{}


% transparency
%%%%%%%%%%%%%%%
\cleartoleftpage

\HugeQuote{S_DISCLOSURE}{All defects are lighter in the open}{. They are most pernicious when concealed beneath a pretense of soundness.}{Seneca}{}{We don't need to post our defects on Facebook, but we can spend some time thinking about them\llink{http://thephilosophersmail.com/PhilosophicalMeditation.pdf}}

\HugeQuote{TF_DISCLOSURE}{Disclosure is disinfectant.}{}{Tim Ferriss}{}{}

% opacity / subtlety
%%%%%%%%%%%%%%%%%%%%%

% \hugeQuote{H_ART}{The art lies in concealing the art.}{}{Horace}{}{} 
% \hugeQuote{M_WORK}{If people knew how hard I worked}{, it would not seem so masterful.}{Michelangelo}{}{}
% \hugeQuote{RG_WORK}{never expose the sweat}{ and labour behind your poise.}{Robert Greene}{}{}

\cleartoleftpage
\HugeQuote{LR_WORK}{It takes a great talent and skill}{ to conceal a great talent and skill.}{Fran\c{c}ois de La Rochefoucauld}{}{} % cf M_WORK

\cleartorightpage
\HugeQuote{FR_DTR}{When you do things right}{, people will wonder if you've done anything at all.}{Computerised space probe, Futurama}{}{} 

