\input{LearningIntro.tex}

\cleartorightpage
\HugeQuote{BH_FP}{The taking of flash photos}{ and the use of recording devices of any kind including; pens, pencils, eyes and ears, is strictly encouraged.}{Bob Holman}{}{}

\cleartorightpage
\HugeQuote{MDM_BOOKS}{Books}{, I find are the best provisions a man can take with him on life's journey.}{Michel de Montaigne}{}{}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cleartoleftpage
\vspace*{\fill}
\hugeQuote{RG_MASTERY}{You must see your attempt at attaining mastery as something necessary and positive.}{}{Robert Greene}{}{}
\hugeQuote{TP_BOOK}{If I read a book}{ and get one good idea from that \$20, then I've gotten one of the greatest deals of all time.}{Tom Peters}{MDM_BOOKS}{}
\vspace*{\fill}
\cleartorightpage
\vspace*{\fill}
\hugeQuote{BF_INVEST}{An investment in knowledge always pays the best interest.}{}{Benjamin Franklin}{}{}
\hugeQuote{RH_LIVE}{Study as if you were going to live forever}{ but live as if you were going to die tomorrow.}{Edmund Rich}{}{}

%Possibly much earlier though.
%\llink{http://bit.ly/2fIQFOc
%https://books.google.co.uk/books?id=95mdmyMC8SsC&dq=%22live+as+if+you+were+to+die+to-morrow%22&pg=PA147&redir_esc=y#v=onepage&q=%22live%20as%20if%20you%20were%20to%20die%20to-morrow%22&f=false
\vspace*{\fill}
\cleartoleftpage
\HugeQuote{AS_FORGET}{To forgive and forget}{ means to have thrown away a dearly bought experience.}{Arthur Schopenhaur}{}{}
\cleartorightpage
\HugeQuote{HST_REACT}{Every reaction is a learning process}{; every significant experience alters your perspective.}{Hunter S. Thompson}{}{}

%\hugeQuote(RHRS}{Reading is not the thing you squeeze in with your other important tasks, it is the important task.}{}{Ryan Holiday}{}{} 

% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cleartoleftpage
\HugeQuote{RG_SOFT}{The greatest danger you face}{ is your mind growing soft and your eyes growing dull.}{Robert Greene}{}{}
\cleartorightpage
\HugeQuote{MR_SOFT}{To let one's mind go lax}{ is, in effect, to lose it.}{Musonius Rufus}{}{}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cleartoleftpage
\vspace*{\fill}
\hugeQuote{BR_CHANGE}{I would never die for my beliefs}{ because I might be wrong.}{Bertand Russell}{}{}
 
\hugeQuote{SW_CHANGE}{The truths he finds}{ may in the comming months or even in the coming years be truths no more.}{Stefan Zwieg}{}{qv. half life of knowledge\footnote{http://bit.ly/2dRSViF}.}
\vspace*{\fill}
\cleartorightpage

\HugeQuote{RH_ML}{More listening}{,\newline 
more learning\newline
Fewer interruptions,\newline
fewer conclusions.
}{Ryan Holiday}{MA_CHANGE}{} % maybe P_TALK

%todo possibly humility 
%cf bertrand russell learning/flowers
\vspace*{\fill}
\hugeQuote{MDM_BOAST}{Does learning mean nothing to you}{ unless you know that someone else knows that you know it?}{Michel de Montaigne}{MC_BOAST}{}

\hugeQuote{E_PIP}{If you didn't learn these things to put them into practice}{, what did you learn them for?}{Epictetus}{}{} 
\vspace*{\fill}
\cleartorightpage
\vspace*{\fill}
\hugeQuote{HST_NOBOAST}{I was not proud of what I had learned}{, but I never doubted that it was worth knowing.}{Hunter S. Thompson}{}{}

\hugeQuote{C_ABILITY}{Ability will never catch up}{ with the demand for it.}{Confucious}{}{}
\vspace*{\fill}
%% mentors
%%%%%%%%%%%%%%%%%%

\cleartoleftpage
\vspace*{\fill}
\smallQuote{RG_TRUST}{Trust yourself more and others less.}{Robert Greene}{}
\smallQuote{WS_TRUST}{Love all.\newline
Trust few.\newline
Do wrong to none.}{William Shakespeare}{}

\smallQuote{MDM_SHEEP}{He who sheep-like follows another follows nothing. He discovers nothing because he seeks nothing.}{Michel de Montaigne}{}
\vspace*{\fill}
\cleartorightpage
\HugeQuote{MI_TRUST}{You'll only get three mentors you can trust}{.\newline
Just make sure you're paying attention so you don't miss them.}{Madalina G. Idomir}{HT_CREDIT}{}


%focus on what's important
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cleartoleftpage
\HugeQuote{NT_NNP}{Never nitpick a heuristic.}{}{Nassim Taleb}{}{}

\cleartorightpage
\HugeQuote{S_FOLLY}{Isn't it the height of folly to learn inessential things}{ when time is so desperately short?}{Seneca}{MA_DL}{}
\cleartoleftpage
\HugeQuote{MDM_WROTE}{To know by heart is not to know}{, it is to keep what they have given youa and store it in your memory}{Michel de Montaigne}{}

\cleartorightpage
\HugeQuote{MDM_MAKE}{It is a greater thing to make oneself impassable}{ than to be impassable as a property of one's nature.}{Michel De Monataigne}{}{}
