\input{PatienceIntro.tex}

%
%%%%%%%%%%%%%%%%%%%%%%%%
\cleartorightpage
\HugeQuote{I_GOAL}{It is more important to know where you're going than to get there quickly.}{}{Isocrates}{MA_GOAL}{}

% timing
%%%%%%%%%%%%%%%%%%%%%%%%
\cleartorightpage
\HugeQuote{ADM_CHARGE}{Ask yourself this question:\newline
Am I in charge of this situation or is this situation in charge of me?}{}{Anthony De Mello}{}

\hugeQuote{ST_WAIT}{Do not make war}{ unless victory may be gained;\newline
If there is a prospect of victory move; \newline
Otherwise, do not.}{Sun Tzu}{}{}

\hugeQuote{BG_NTL}{Never contend with a man who has nothing to lose}{.}{Baltazar Gra\c{c}ian}{}{}

\hugeQuote{RG_WAIT2}{If you are unsure of a course of action do not attempt it}{.\newline
Your doubts and hestitation will infect your execution.}{Robert Greene}{}{}

\hugeQuote{RG_WAIT1}{Impatience}{: perhaps the single greatest pitfall.}{Robert Greene}{}{}

%judgement
%%%%%%%%%%%%%%%%%%%%%%%%
\cleartoleftpage
\hugeQuote{UG_COUNT}{There are always more of them}{ before they are counted.}{Ulysses S Grant}{RH_ENDURE}{}

\hugeQuote{WG_JUDGE}{The senses don't decieve}{, judgement deceives.}{John Von Goethe}{}{}

\cleartorightpage
\HugeQuote{E_DLTF}{Don't let the force of impressions knock you off your feet}{; just say to it \say{Just hold on a minute, let me see who you are and what you represent. Let me put you to the test.}}{Epictetus}{}{}


% think before you speak
%%%%%%%%%%%%%%%%%%%%%%%%
\cleartoleftpage

\hugeQuote{RG_TALK}{Once the words are out}{, you cannot take them back. }{Robert Greene}{}{}
\hugeQuote{RH_TALK}{The best advice I ever got}{ was \say{shut up}}{Ryan Holiday}{}{\href{http://tcat.tc/1IwHzGd}{http://tcat.tc/1IwHzGd}}
% \smallQuote{LT_SL}{Those who know don't talk.\newline
% Those who talk don't know.}{Lao Tzu}{}{}
\hugeQuote{LT_SL}{Spare words}{: nature's way. Violent winds do not blow all morning.}{Lao Tzu}{}

\cleartorightpage
\HugeQuote{P_TALK}{Wise men speak because they have something to say}{; fools because they have to say something.}{Plato}{}{}


%todo unsure, maybe generosity
%%%%%%%%%%%%%%%%%%%%%%%%
% \hugeQuote{H_LIGHT}{Light cares can talk}{ huge ones are strick dumb}{Hippolitus}{}{}
% compare people posting on FB vs being truly dumbstruck at events
% more like generosity but certainly an element of patience needed 
% for the first class
%%%%%%%%%%%%%%%%%%%%%%%%

%temper
%%%%%%%%%%%%%%%%%%%%%%%%

\cleartoleftpage
% \hugeQuote{LT_ANGER}{The best fighter is never angry.}{}{Lao Tzu}{}
\smallQuote{LT_BF}{The good soldier is not hot-tempered.}{Lao Tzu}{}

\smallQuote{BG_ANGER}{Never do anything when you are in a temper, for you will do everything wrong.}{Baltazar Gra\c{c}ian}{}

\smallQuote{RG_ANGER}{Anger and emotion are strategically counterproductive. You must always stay calm and objective}{Robert Greene}{}

\smallQuote{MA_GRIEF}{How much more damage grief and anger do than the things that caused them.}{Marcus Aurelius}{}

\cleartorightpage
\HugeQuote{AM_FEAR}{Fear is a bad advisor.}{}{Angela Merkel}{}{}


