\input{ResilienceIntro.tex}

\cleartorightpage

\HugeQuote{JP_STAND}{Fall seven times}{, stand eight}{Japanese Proverb}{MA_PERSIST2}{}

%% calm minds
\cleartoleftpage

\smallQuote{CD_PROMISE}{Promise yourself to be so strong that nothing can disturb your peace of mind.}{Christian D'Larson}{}{}

\smallQuote{FN_TIRED}{When we are tired we are attacked by ideas we conquered long ago.}{Friedrich Nietzche}{}

\smallQuote{CN_MEAT}{All the meat and all that it wants.}{Case, Neuromancer}{}

\smallQuote{SP_FAT}{It's just fat and muscle.}{}{}


%
%%%%%%%%%%%%%
%TODO: position ? 
\hugeQuote{MA_CONTROL2}{We control our own actions}{ and are responsible for them. If we act wrongly we have done serious harm to ourselves.}{Marcus Aurelius}{}{}

\hugeQuote{MA_DWH}{Does what happened}{ stop you from acting with justice, generosity, self control, sanity, prudence, honesty and straight forwardness?}{Marcus Aurelius}{}{}


%% haters gonna hate
%%%%%%%%%%%%%%%%%%%%
\cleartoleftpage
\smallQuote{TS_HHH}{Haters gonna hate, hate, hate, hate, hate.}{Taylor Swift}{MA_HATE}{}
\smallQuote{S_BTR}{The world loves to blacken the radiant and drag the sublime through the dust.}{Schiller}{}{}

\smallQuote{MA_SANITY}{Ambition: tying your well being to what other people say and do.\newline
Self-indulgence: tying it to the things that happen to you.\newline
Sanity: tying it to your own actions.}{Marcus Aurelius}{ST_UTU}{}

\cleartorightpage
\hugeQuote{DLP_DNA}{You don't need their approval.}{}{Danielle La Porte}{}{}

\hugeQuote{MA_TC}{Tranquility comes when you stop caring what they say.}{}{Marcus Aurelius}{}{}

\hugeQuote{MA_HARM1}{Choose not to be harmed}{ and you won't feel harmed.\newline
Don't feel harmed and you haven't been.}{Marcus Aurelius}{}{}
\hugeQuote{MA_HARM2}{It can ruin your life}{ only if it ruins your character. Otherwise it cannot harm you. Inside or out.}{Marcus Aurelius}{}{}

\hugeQuote{MA_ALONE}{Everyone gets one life.}{ Your's is almost used up and instead of treating yourself with respect you have entrusted your happiness to others.}{Marcus Aurelius}{}{}

\cleartorightpage
\HugeQuote{LT_SANITY}{Care about what other people think}{ and you will always be their prisoner.}{Lao Tzu}{ST_UTU}{}

%%what is up to us
%%%%%%%%%%%%%%%%%%%
\cleartoleftpage

\smallQuote{MR_UTU}{If you work hard to do what is right, do not be upset by roadblocks; think about how many of the things in your life haven't turned out as you wanted them to but as they should have done.}{Musonius Rufus}{} 

\smallQuote{RH_EFFORT}{You control the effort not the results.}{Ryan Holiday}{}{}

\cleartorightpage
\HugeQuote{ST_UTU}{Ta eph'hemin}{\newline
Ta ouk eph'hemin}{Stoic phrase}{}{what is up to us, what is not up to us.}

%TODO: location ? 
\hugeQuote{MA_STR}{Straight not straightened}{}{Marcus Aurelius}{}{}
\hugeQuote{MA_MIND1}{What is outside my mind}{ means nothing to it}{Marcus Aurelius}{}{}
\hugeQuote{MA_MIND2}{The mind without passions}{ is like a fortress. No place is more secure}{Marcus Aurelius}{}{}


%% observation vs perception
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cleartoleftpage
\hugeQuote{WS_PROBLEMS}{Nothing either good nor bad}{ but thinking makes it so.}{William Shakespeare}{}{}

\hugeQuote{TNV_PROBLEMS}{Real difficulties can be overcome.}{\newline 
It's only the imaginary ones that are unconquerable.}{Theodore N Vail}{UG_COUNT}{}

\hugeQuote{RH_PROBLEMS}{Problems are rarely as bad as we think they are}{, or rather, they are precisely as bad as we think they are.}{Ryan Holiday}{MA_JUDGE}{}

\hugeQuote{MA_PROBLEMS}{External things are not the problem.}{ It's your assessment of them which you can erase right now.}{Marcus Aurelius}{}{}

% \hugeQuote{RH_ENDURE}{See things for what they are,}{do what we can, endure what we must}{Ryan Holiday}{}{} % taken from schenhauer


%% Endure
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cleartoleftpage
\hugeQuote{S_ENDURE}{Not to give in}{to adversity.\newline
Not to trust prosperity.\newline \newline
And always take note of Fortune's habit of behaving exactly as she pleases.}{Seneca}{}{}

% \hugeQuote{MA_PERSIST1}{So keep at it}{ until it's fully digested. A strong stomach digests whatever it eats. A blazing fire takes whatever you throw on it and makes light and flame.}{Marcus Aurelius}{CP_FAIL}{}

\hugeQuote{MAR_PERSIST}{Courage doesn't always roar.}{ Sometimes courage is the quiet voice at the end of the day whispering: \newline \say{I will try again tomorrow.}}{Mary Anne Radmach}{CP_FAIL}{}

\hugeQuote{MA_PERSIST2}{Disgraceful}{ for the soul to give up while the body is still going strong}{Marcus Aurelius}{}{}

\cleartoleftpage
\hugeQuote{H_CHANGE}{Change is the only constant in life.}{}{Heraclitus}{}{}

\hugeQuote{JM_CHANGE}{You can suffer}{ the pain of change or suffer remaining the way you are.}{Joyce Meyer}{}{}

\cleartorightpage
\HugeQuote{JKZ_ENDURE}{You can't stop the waves}{ but you can learn how to surf}{Jon Kabat Zin}{H_CHANGE}{}

%% Solitude
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\smallQuote{JB_ALONE}{All of our unhappiness comes from our inability to be alone.}{Jean de la Brugere}{}{}
% \smallQuote{GVG_ALONE}{A bore is someone who deprives you of solitude without providing you with company}{Gian Vincenzo Gravina}{}{}
% \smallQuote{RG_ALONE}{Strive to keep yourself free from unnecessary entanglements and alliances.}{Robert Greene}{}{}

\smallQuote{AS_ALONE}{The more a man has in himself, the less others can be to him.}{Arthur Schopenhauer}{} 
% \smallQuote{RWE_ALONE}{Nothing can bring you peace but yourself.\newline
% Nothing can bring you peace but the triumph of principles}{Ralph Waldo Emerson}{}
\smallQuote{LT_CH}{He who conquers others is strong, he who conquers himself is mighty.}{Lao Tzu}{}{}

\smallQuote{H_TRAVEL}{It is reason and wisdom which take away cares not places affording views over the sea.}{Horace}{}

\cleartorightpage
\HugeQuote{A_ALONE}{Happiness depends on ourselves.}{}{Aristotle}{}{}

%% planning for failure and NV
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cleartoleftpage
\smallQuote{CF_SUCCESS}{Success depends on previous preparation, and without such preparation there can be no success}{Confucius}{}

\smallQuote{PPPPP}{Proper planning prevents piss poor performance}{}{}

\cleartorightpage
\hugeQuote{OS_OPTIMISM}{Optimism is cowardice}{}{Oswald Spengler}{}{}
\hugeQuote{HOPE}{Hope is a poor hedge}{}{Erik R. Sirri}{}{2007, but likely earlier}

\cleartoleftpage
\HugeQuote{HA_PREPARE}{This is the precept by which I have lived}{:\newline
Prepare for the worst,\newline 
expect the best \newline
and take what comes.}{Hannah Ardent}{}{}

\cleartorightpage
\HugeQuote{SP_LUCK}{Preparation}{ not luck}{}{}{}

%% mentors
%%%%%%%%%%%%%%%%%%

\cleartoleftpage
\smallQuote{RG_TRUST}{Trust yourself more and others less.}{Robert Greene}{}
\smallQuote{WS_TRUST}{Love all.\newline
Trust a few.\newline
Do wrong to none.}{William Shakespeare}{}
%TODO: check w/maddie for wording 
%\smallQuote{MI_TRUST}{You'll get three mentors you can trust.}{Madalina Idomir}{from her teacher, but we'll share the credit (\S \ref{HT_CREDIT}).}

%% Luck and Fates

\cleartorightpage
\HugeQuote{MA_LUCK2}{I was once a fortunate man}{, then fortune deserted me but true good fortune is what you make for yourself.

Good fortune:
\begin{itemize}
  \item good character
  \item good intentions
  \item good actions
\end{itemize}}
{Marcus Aurelius}{E_LUCK}{}

%% judgement
%%%%%%%%%%%%%%%%%%%%%%%

\hugeQuote{MA_NOW3}{Objective judgment}{ now, at this very moment.

Unselfish action now, at this very moment.

Willing acceptance of all external events now, at this very moment.

That's all you need}{Marcus Aurelius}{}{}

\hugeQuote{MA_JUDGE}{It is we who generate the judgments}{ inscribing them on ourselves}{Marcus Aurelius}{}{}

\hugeQuote{WD_JUDGE}{When you judge another}{ you do not define them, you define yourself.}{Wayne Dyer}{}{}

\cleartorightpage
\HugeQuote{TT_BURDEN}{The burden is equal to the strength of the horse.}{}{The Talmud}{}{}


